
ANALYZING THE EFFECT OF VIOLENT VIDEO GAME PLAY ON MATE VALUE AND OTHER MATING RELATED VARIABLES
========================================================

General housekeeping
--------------------

First load the libraries that we are using
```{r}
library(ggplot2)
library(knitr)
library(plyr)
library(tidyr)
library(patchwork)
library(ggstance)
```

Load the data (All_Experiments.csv).
Note the as.is thing which leaves all the character vectors as strings and does not make them into factors.

```{r}
data = read.csv("All_Experiments.csv")
```

Attach and check the headers of each column

```{r}
names(data)
```

Delete Rows where participants were unable to load or play game, had issues with the survey loading, or failed an attention check (144 people). Also delete rows where participants recorded gender as "Other" (2 people).

```{r}
data<-data[-which(data$Removedata == "Yes"), ]
data<-data[-which(data$Sex == "Other"), ]
```


Remove individuals that have a relationship status of 'other' (13 individuals)

```{r}
data = subset(data, Relationshipstatus %in% c("Single", "In an open relationship/casually dating", "In a long-term monogamous relationship eg. married, partnered", "Recently single/divorced/separated"))
```

Subset data into the three experiments
```{r}
data_gaming = subset(data, study=="Gaming_manipulation")
data_rank = subset(data, study=="Rank_manipulation")
data_faces = subset(data, study=="Face_choice")
```
---------------

---------------
First, check the distributions of all the variables of interest
```{r}
ggplot(data,aes(x=MV1Total,group=study,fill=study))+
  geom_histogram(position="dodge",binwidth=1)+theme_bw()

ggplot(data,aes(x=MV2Average,group=study,fill=study))+
  geom_histogram(position="dodge",binwidth=0.5)+theme_bw()

ggplot(data,aes(x=SGAAverage,group=study,fill=study))+
  geom_histogram(position="dodge",binwidth=0.5)+theme_bw()

ggplot(data,aes(x=HostilityTotal,group=study,fill=study))+
  geom_histogram(position="dodge",binwidth=0.5)+theme_bw()

ggplot(data,aes(x=SOIRTOTAL,group=study,fill=study))+
  geom_histogram(position="dodge",binwidth=10)+theme_bw()

ggplot(data,aes(x=Kinsey,group=study,fill=study))+
  geom_histogram(position="dodge",binwidth=1)+theme_bw()
```

The distributions for all of them are fine, except for Hostility Total. HT specifically has very little variation in it, so I don't think it will be very useful and am happy to remove it from the models.

What is the mean, SD and range of the age of respondents in each study?
```{r}
ddply(data,~study,summarise,mean=mean(Age),sd=sd(Age), min=min(Age), max=max(Age))
```

How many men and women, and their relationship details
```{r}
table(data_gaming$Sex)
table(data_rank$Sex)
table(data_faces$Sex)

table(data_gaming$Relationshipstatus)
table(data_rank$Relationshipstatus)
table(data_faces$Relationshipstatus)
```

Exploration of between study differences
----------------------------------------

Do men and women differ in the amount of violent video games they play (self-rated)

```{r}
VVGDemo <- lm(Averagefrequencyviolence ~  Age + Sex + study + Age*Sex + study*Sex + study*Age, data=data)
anova(VVGDemo, test="Chisq")
summary(VVGDemo, test="Chisq")

```

HISTOGRAM
```{r}
ggplot(data, aes(x=study, y=Averagefrequencyviolence, fill=Sex)) + geom_violin() + 
  xlab("Sex") +
  ylab("Self-rated performance") +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())



ggplot(data, aes(x=Averagefrequencyviolence, fill=Sex)) + 
  geom_histogram(binwidth=2, position="dodge") +
  xlab("Self-rated Violence Exposure") +
  ylab("Count") +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  theme(axis.line = element_line(colour = "black"),
        plot.title = element_text(size=30, face="bold"),
        legend.position = "right",
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

gaming_hist <- ggplot(data_gaming, aes(x=Averagefrequencyviolence, fill=Sex)) + 
  geom_histogram(binwidth=2, position="dodge") +
  xlab("Self-rated Violence Exposure") +
  ylab("Count") +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  theme(axis.line = element_line(colour = "black"),
        plot.title = element_text(size=30, face="bold"),
        legend.position = "right",
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

rank_hist <- ggplot(data_rank, aes(x=Averagefrequencyviolence, fill=Sex)) + 
  geom_histogram(binwidth=2, position="dodge") +
  xlab("Self-rated Violence Exposure") +
  ylab("Count") +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  theme(axis.line = element_line(colour = "black"),
        plot.title = element_text(size=30, face="bold"),
        legend.position = "right",
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

face_hist <- ggplot(data_faces, aes(x=Averagefrequencyviolence, fill=Sex)) + 
  geom_histogram(binwidth=2, position="dodge") +
  xlab("Self-rated Violence Exposure") +
  ylab("Count") +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  theme(axis.line = element_line(colour = "black"),
        plot.title = element_text(size=30, face="bold"),
        legend.position = "right",
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 


```

Relationship between Age, Sex, and Exposure to violence:
```{r}
ggplot(data, aes(x = Age, y = Averagefrequencyviolence, color = Sex, linetype = Sex)) + 
  geom_point(shape = 0, size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("Violent Video Game Exposure") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 
```

Experiment 1: Gaming Manipulation
---------------------------------

Do men and women differ in how well they performed in the game in both self-rated (selfscore) and actual performance

```{r}
Perf <- lm(Selfscore ~  Age + Sex + VorNV + Averagefrequencyviolence + Age*VorNV + Sex*VorNV, data = data_gaming)
anova(Perf, test="Chisq")
summary(Perf, test="Chisq")

ddply(data_gaming,~Sex,summarise,mean=mean(Selfscore),sd=sd(Selfscore), se=sd(Selfscore)/sqrt(length(Selfscore)))
ddply(data_gaming,~VorNV,summarise,mean=mean(Selfscore),sd=sd(Selfscore), se=sd(Selfscore)/sqrt(length(Selfscore)))

```

Effect sizes
```{r}
effect.size(data_gaming$Selfscore, data_gaming$, pooled = TRUE, conf.level = 0.95)
```

##MANOVA
```{r}
MANOVA_gaming<- manova(cbind(MV1Total, SGAAverage, SOIRTOTAL) ~ Age + Sex + VorNV + Averagefrequencyviolence + Selfscore +  VorNV*Selfscore + VorNV*Sex + Age*Sex, data=data_gaming)
summary(MANOVA_gaming, test="Pillai")
summary.aov(MANOVA_gaming)
```

Experiment 2: Rank Manipulation
---------------------------------

Are self-scores correlated with the rank they are randomly given in the game

```{r}
selfrank_corr <- lm(Selfscore  ~  Age + Sex + VorNV + Averagefrequencyviolence + Rank + Age*VorNV + Sex*VorNV + Rank*Sex + Rank*VorNV, data = data_rank)
anova(selfrank_corr, test="Chisq")

ddply(data_rank, .(Sex), summarize, mean=mean(Selfscore), se=sd(Selfscore)/sqrt(length(Selfscore)))

```

##MANOVA
```{r}
MANOVA_rank<- manova(cbind(MV1Total, SGAAverage, SOIRTOTAL) ~ Age + Sex + VorNV + Averagefrequencyviolence + Selfscore + Rank + VorNV*Selfscore + VorNV*Sex + Age*Sex + VorNV*Rank, data=data_rank)

summary(MANOVA_rank, test="Pillai")
summary.aov(MANOVA_rank)

ddply(data_rank, .(Sex), summarize, mean=mean(SGAAverage), se=sd(SGAAverage)/sqrt(length(SGAAverage)))
ddply(data_rank, .(Sex), summarize, mean=mean(SOIRTOTAL), se=sd(SOIRTOTAL)/sqrt(length(SOIRTOTAL)))

```


Experiment 3: Face Choices
---------------------------------

Do men and women differ in how well they performed in the game in both self-rated (selfscore) and actual performance

```{r}
Perf <- lm(Selfscore ~  Age + Sex + VorNV + Averagefrequencyviolence + Age*VorNV + Sex*VorNV, data = data_faces)
anova(Perf, test="Chisq")
summary(Perf, test="Chisq")

ddply(data_faces, .(Sex), summarize, mean=mean(Selfscore), se=sd(Selfscore)/sqrt(length(Selfscore)))
ddply(data_faces, .(VorNV), summarize, mean=mean(Selfscore), se=sd(Selfscore)/sqrt(length(Selfscore)))

data_faces_fem = subset(data_faces, Sex=="Female")
data_faces_mal = subset(data_faces, Sex=="Male")

ddply(data_faces_mal, .(VorNV), summarize, mean=mean(Selfscore), se=sd(Selfscore)/sqrt(length(Selfscore)))

```


##MANOVA
```{r}
MANOVA_face<- manova(cbind(MV1Total, SGAAverage, SOIRTOTAL) ~ Age + Sex + VorNV + Averagefrequencyviolence + Selfscore + VorNV*Selfscore + VorNV*Sex + Age*Sex, data=data_faces)

summary(MANOVA_face, test="Pillai")
summary.aov(MANOVA_face)

ddply(data_rank, .(Sex), summarize, mean=mean(MV1Total), se=sd(MV1Total)/sqrt(length(MV1Total)))
ddply(data_rank, .(Sex), summarize, mean=mean(SOIRTOTAL), se=sd(SOIRTOTAL)/sqrt(length(SOIRTOTAL)))

```


Short term faces: 

```{r}
STselection <- lm(TotalSTScore ~  Age + Sex + VorNV + Averagefrequencyviolence + Selfscore + Sex*Selfscore, data=data_faces)

anova(STselection)
```


```{r}
LTselection <- lm(TotalLTScore ~  Age + Sex + VorNV + Averagefrequencyviolence + Selfscore + Sex*Selfscore, data=data_faces)

anova(LTselection)
```

Figures
-------

Any figure with 3 panels is saved at 1400 width

Figure 1: The relationship between the self-perception of a participant's performance and their age, separately for each sex in each experiment.

```{r}
Figure1a <- ggplot(data_gaming, aes(x = Age, y = Selfscore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(position=ggstance::position_dodgev(height=0.3), size = 4) + 
  scale_x_continuous(breaks=c(10,20,30,40,50,60,70), limits=c(15,75)) +
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7), limits=c(0.75,7)) +
  scale_colour_hue(l=50) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("Self-perceived performance") +
  labs(title = "Experiment 1") +
    theme(axis.line = element_line(colour = "black"),
        legend.position="none",  
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        plot.title = element_text(hjust = 0.5, size = 22, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure1b <- ggplot(data_rank, aes(x = Age, y = Selfscore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(position=ggstance::position_dodgev(height=0.3), size = 4) + 
  scale_x_continuous(breaks=c(10,20,30,40,50,60,70), limits=c(15,75)) +
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7), limits=c(0.75,7)) +
  scale_colour_hue(l=50) +
  guides(fill=FALSE) + 
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("") +
  labs(title = "Experiment 2") +
    theme(axis.line = element_line(colour = "black"),
        legend.position="none", 
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = -20, b = 0, l = 0)),
        plot.title = element_text(hjust = 0.5, size = 22, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure1c <- ggplot(data_faces, aes(x = Age, y = Selfscore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(position=ggstance::position_dodgev(height=0.3), size = 4) + 
  scale_x_continuous(breaks=c(10,20,30,40,50,60,70), limits=c(15,75)) +
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7), limits=c(0.75,7)) +
  scale_colour_hue(l=50) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("") +
  labs(title = "Experiment 3") +
    theme(axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = -20, b = 0, l = 0)),
        plot.title = element_text(hjust = 0.5, size = 22, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

Figure1a + Figure1b + Figure1c
```


Figure 2: The self-perception of performance as a function of their treatment across all three experiments. 

```{r}
Figure2a <- ggplot(data_gaming, aes(x=VorNV, y=Selfscore)) + geom_violin(lwd=1) + 
  xlab("") +
  ylab("Self-perceived performance") +
  scale_x_discrete(labels=c("NV" = "Non-Violent", "V" = "Violent")) +
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7), limits=c(0.75,7)) +
  geom_boxplot(lwd=1, width=0.1) +
  labs(title = "Experiment 1") +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=14),
        axis.title=element_text(size=16,face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        plot.title = element_text(hjust = 0.5, size = 16, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

Figure2b <- ggplot(data_rank, aes(x=VorNV, y=Selfscore)) + geom_violin(lwd=1) + 
  xlab("Game Treatment") +
  ylab("") +
  scale_x_discrete(labels=c("NV" = "Non-Violent", "V" = "Violent")) +
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7), limits=c(0.75,7)) +
  geom_boxplot(lwd=1, width=0.1) +
  labs(title = "Experiment 2") +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=14),
        axis.title=element_text(size=16,face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = -20, b = 0, l = 0)),
        plot.title = element_text(hjust = 0.5, size = 16, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure2c <- ggplot(data_faces, aes(x=VorNV, y=Selfscore)) + geom_violin(lwd=1) + 
  xlab("") +
  ylab("") +
  scale_x_discrete(labels=c("NV" = "Non-Violent", "V" = "Violent")) +
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7), limits=c(0.75,7)) +
  geom_boxplot(lwd=1, width=0.1) +
  labs(title = "Experiment 3") +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=14),
        axis.title=element_text(size=16,face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = -20, b = 0, l = 0)),
        plot.title = element_text(hjust = 0.5, size = 16, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure2a + Figure2b + Figure2c
```

Figure 3: The relationship between the self-perception of a participant's performance and their exposure to violence, separately for each sex in each experiment.

```{r}
Figure3a <- ggplot(data_gaming, aes(x = Averagefrequencyviolence, y = Selfscore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(position=ggstance::position_dodgev(height=0.3), size = 4) + 
  scale_x_continuous(breaks=c(0,10,20,30,40,50), limits=c(0,50)) +
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7), limits=c(0.75,7)) +
  scale_colour_hue(l=50) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("") +
  ylab("Self-perceived performance") +
  labs(title = "Experiment 1") +
    theme(axis.line = element_line(colour = "black"),
        legend.position="none",  
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        plot.title = element_text(hjust = 0.5, size = 22, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure3b <- ggplot(data_rank, aes(x = Averagefrequencyviolence, y = Selfscore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(position=ggstance::position_dodgev(height=0.3), size = 4) + 
  scale_x_continuous(breaks=c(0,10,20,30,40,50), limits=c(0,50)) +
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7), limits=c(0.75,7)) +
  scale_colour_hue(l=50) +
  guides(fill=FALSE) + 
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Exposure to violence") +
  ylab("") +
  labs(title = "Experiment 2") +
    theme(axis.line = element_line(colour = "black"),
        legend.position="none", 
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = -20, b = 0, l = 0)),
        plot.title = element_text(hjust = 0.5, size = 22, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure3c <- ggplot(data_faces, aes(x = Averagefrequencyviolence, y = Selfscore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(position=ggstance::position_dodgev(height=0.3), size = 4) + 
  scale_x_continuous(breaks=c(0,10,20,30,40,50), limits=c(0,50)) +
  scale_y_continuous(breaks=c(1,2,3,4,5,6,7), limits=c(0.75,7)) +
  scale_colour_hue(l=50) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("") +
  ylab("") +
  labs(title = "Experiment 3") +
    theme(axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = -20, b = 0, l = 0)),
        plot.title = element_text(hjust = 0.5, size = 22, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

Figure3a + Figure3b + Figure3c
```


Figure 4: The relationship between the self-perceived mate value and self-perception of a participant's performance, separately for each sex in each experiment.

```{r}
Figure4a <- ggplot(data_gaming, aes(x = Selfscore, y = MV1Total, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(position=position_dodge(width=0.8), size = 4) + 
  scale_x_continuous(breaks=c(1,2,3,4,5,6,7), limits=c(0.75,7)) +
  scale_y_continuous(breaks=c(0,5,10,15,20,25,30), limits=c(0,30)) +
  scale_colour_hue(l=50) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("") +
  ylab("Self-perceived mate value") +
  labs(title = "Experiment 1") +
    theme(axis.line = element_line(colour = "black"),
        legend.position="none",  
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        plot.title = element_text(hjust = 0.5, size = 22, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure4b <- ggplot(data_rank, aes(x = Selfscore, y = MV1Total, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(position=position_dodge(width=0.8), size = 4) + 
  scale_x_continuous(breaks=c(1,2,3,4,5,6,7), limits=c(0.75,7)) +
  scale_y_continuous(breaks=c(0,5,10,15,20,25,30), limits=c(0,30)) +
  scale_colour_hue(l=50) +
  guides(fill=FALSE) + 
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Self-perceived performance") +
  ylab("") +
  labs(title = "Experiment 2") +
    theme(axis.line = element_line(colour = "black"),
        legend.position="none", 
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = -20, b = 0, l = 0)),
        plot.title = element_text(hjust = 0.5, size = 22, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure4c <- ggplot(data_faces, aes(x = Selfscore, y = MV1Total, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(position=position_dodge(width=0.8), size = 4) + 
  scale_x_continuous(breaks=c(1,2,3,4,5,6,7), limits=c(0.75,7)) +
  scale_y_continuous(breaks=c(0,5,10,15,20,25,30), limits=c(0,30)) +
  scale_colour_hue(l=50) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("") +
  ylab("") +
  labs(title = "Experiment 3") +
    theme(axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = -20, b = 0, l = 0)),
        plot.title = element_text(hjust = 0.5, size = 22, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

Figure4a + Figure4b + Figure4c
```


Figure 5: The relationship between the Sociosexual Inventory and self-perception of a participant's performance, separately for each sex in each experiment.

```{r}
Figure5a <- ggplot(data_gaming, aes(x = Age, y = SOIRTOTAL, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_x_continuous(breaks=c(10,20,30,40,50,60,70,80), limits=c(18,80)) +
  scale_y_continuous(breaks=c(0,10,20,30,40,50,60,70,80), limits=c(5,85)) +
  scale_colour_hue(l=50) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("") +
  ylab("Sociosexual Inventory") +
  labs(title = "Experiment 1") +
    theme(axis.line = element_line(colour = "black"),
        legend.position="none",  
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        plot.title = element_text(hjust = 0.5, size = 22, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure5b <- ggplot(data_rank, aes(x = Age, y = SOIRTOTAL, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_x_continuous(breaks=c(10,20,30,40,50,60,70,80), limits=c(18,80)) +
  scale_y_continuous(breaks=c(0,10,20,30,40,50,60,70,80), limits=c(5,85)) +
  scale_colour_hue(l=50) +
  guides(fill=FALSE) + 
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Self-perceived performance") +
  ylab("") +
  labs(title = "Experiment 2") +
    theme(axis.line = element_line(colour = "black"),
        legend.position="none", 
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = -20, b = 0, l = 0)),
        plot.title = element_text(hjust = 0.5, size = 22, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure5c <- ggplot(data_faces, aes(x = Age, y = SOIRTOTAL, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_x_continuous(breaks=c(10,20,30,40,50,60,70,80), limits=c(18,80)) +
  scale_y_continuous(breaks=c(0,10,20,30,40,50,60,70,80), limits=c(5,85)) +
  scale_colour_hue(l=50) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("") +
  ylab("") +
  labs(title = "Experiment 3") +
    theme(axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = -20, b = 0, l = 0)),
        plot.title = element_text(hjust = 0.5, size = 22, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

Figure5a + Figure5b + Figure5c
```

Figure 6: 

```{r}
Figure6a <- ggplot(data_faces, aes(x = Selfscore, y = TotalSTScore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(position=ggstance::position_dodgev(height=0.4), size = 4) + 
  scale_colour_hue(l=50) +
  scale_x_continuous(breaks=c(0,1,2,3,4,5,6,7), limits=c(0,7)) +
  scale_y_continuous(breaks=c(0,1,2,3,4,5,6), limits=c(0,6)) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Self-perceived performance") +
  ylab("Preference for masculine faces") + 
  labs(title = "Short-term") +
  theme(axis.line = element_line(colour = "black"),
        legend.position="none",
        axis.text=element_text(size=16),
        axis.title=element_text(size=20,face="bold"),
        plot.title = element_text(hjust = 0.5, size = 22, face="bold"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure6b <- ggplot(data_faces, aes(x = Age, y = TotalLTScore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(position=ggstance::position_dodgev(height=0.4), size = 4) + 
  scale_colour_hue(l=50) +
  scale_x_continuous(breaks=c(10,20,30,40,50,60,70,80), limits=c(18,80)) +
  scale_y_continuous(breaks=c(0,1,2,3,4,5,6), limits=c(0,6)) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("") + 
  labs(title = "Long-term") +
  theme(axis.line = element_line(color = "black"),
        axis.text=element_text(size=16),
        axis.title=element_text(size=20,face="bold"),
        plot.title = element_text(hjust = 0.5, size = 22, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure6a + Figure6b
```
