
ANALYZING THE EFFECT OF VIOLENT VIDEO GAME PLAY ON MATE VALUE AND OTHER MATING RELATED VARIABLES
========================================================

General housekeeping
--------------------

First load the libraries that we are using
```{r}
library(ggplot2)
library(knitr)
library(plyr)
library(tidyr)
```

Load the data (All_Experiments.csv).
Note the as.is thing which leaves all the character vectors as strings and does not make them into factors.

```{r}
data = read.csv("All_Experiments.csv")
```

Attach and check the headers of each column

```{r}
names(data)
```

Delete Rows where participants were unable to load or play game, had issues with the survey loading, or failed an attention check (144 people). Also delete rows where participants recorded gender as "Other" (2 people).

```{r}
data<-data[-which(data$Removedata == "Yes"), ]
data<-data[-which(data$Sex == "Other"), ]
```


Remove individuals that have a relationship status of 'other' (13 individuals)

```{r}
data = subset(data, Relationshipstatus %in% c("Single", "In an open relationship/casually dating", "In a long-term monogamous relationship eg. married, partnered", "Recently single/divorced/separated"))
```

Subset data into the three experiments
```{r}
data_gaming = subset(data, study=="Gaming_manipulation")
data_rank = subset(data, study=="Rank_manipulation")
data_faces = subset(data, study=="Face_choice")
```
---------------
Adding in any functions

Multiple plot function

ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
- cols:   Number of columns in layout
- layout: A matrix specifying the layout. If present, 'cols' is ignored.
If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
then plot 1 will go in the upper left, 2 will go in the upper right, and
3 will go all the way across the bottom.
```{r}

multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

---------------
First, check the distributions of all the variables of interest
```{r}
ggplot(data,aes(x=MV1Total,group=study,fill=study))+
  geom_histogram(position="dodge",binwidth=1)+theme_bw()

ggplot(data,aes(x=MV2Average,group=study,fill=study))+
  geom_histogram(position="dodge",binwidth=0.5)+theme_bw()

ggplot(data,aes(x=SGAAverage,group=study,fill=study))+
  geom_histogram(position="dodge",binwidth=0.5)+theme_bw()

ggplot(data,aes(x=HostilityTotal,group=study,fill=study))+
  geom_histogram(position="dodge",binwidth=0.5)+theme_bw()

ggplot(data,aes(x=SOIRTOTAL,group=study,fill=study))+
  geom_histogram(position="dodge",binwidth=10)+theme_bw()

ggplot(data,aes(x=Kinsey,group=study,fill=study))+
  geom_histogram(position="dodge",binwidth=1)+theme_bw()
```

The distributions for all of them are fine, except for Hostility Total. HT specifically has very little variation in it, so I don't think it will be very useful and am happy to remove it from the models.

What is the mean, SD and range of the age of respondents in each study?
```{r}
ddply(data,~study,summarise,mean=mean(Age),sd=sd(Age), min=min(Age), max=max(Age))
```

How many men and women, and their relationship details
```{r}
table(data_gaming$Sex)
table(data_rank$Sex)
table(data_faces$Sex)

table(data_gaming$Relationshipstatus)
table(data_rank$Relationshipstatus)
table(data_faces$Relationshipstatus)
```

Exploration of between study differences
----------------------------------------

Do men and women differ in the amount of violent video games they play (self-rated)

```{r}
VVGDemo <- lm(Averagefrequencyviolence ~  Age + Sex + study + Age*Sex + study*Sex + study*Age, data=data)
anova(VVGDemo, test="Chisq")
summary(VVGDemo, test="Chisq")

```

HISTOGRAM
```{r}
ggplot(data, aes(x=study, y=Averagefrequencyviolence, fill=Sex)) + geom_violin() + 
  xlab("Sex") +
  ylab("Self-rated performance") +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())



ggplot(data, aes(x=Averagefrequencyviolence, fill=Sex)) + 
  geom_histogram(binwidth=2, position="dodge") +
  xlab("Self-rated Violence Exposure") +
  ylab("Count") +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  theme(axis.line = element_line(colour = "black"),
        plot.title = element_text(size=30, face="bold"),
        legend.position = "right",
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

gaming_hist <- ggplot(data_gaming, aes(x=Averagefrequencyviolence, fill=Sex)) + 
  geom_histogram(binwidth=2, position="dodge") +
  xlab("Self-rated Violence Exposure") +
  ylab("Count") +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  theme(axis.line = element_line(colour = "black"),
        plot.title = element_text(size=30, face="bold"),
        legend.position = "right",
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

rank_hist <- ggplot(data_rank, aes(x=Averagefrequencyviolence, fill=Sex)) + 
  geom_histogram(binwidth=2, position="dodge") +
  xlab("Self-rated Violence Exposure") +
  ylab("Count") +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  theme(axis.line = element_line(colour = "black"),
        plot.title = element_text(size=30, face="bold"),
        legend.position = "right",
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

face_hist <- ggplot(data_faces, aes(x=Averagefrequencyviolence, fill=Sex)) + 
  geom_histogram(binwidth=2, position="dodge") +
  xlab("Self-rated Violence Exposure") +
  ylab("Count") +
  scale_x_continuous(expand = c(0, 0)) + scale_y_continuous(expand = c(0, 0)) +
  theme(axis.line = element_line(colour = "black"),
        plot.title = element_text(size=30, face="bold"),
        legend.position = "right",
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

multiplot(gaming_hist, rank_hist, face_hist, cols=1)
```

Relationship between Age, Sex, and Exposure to violence:
```{r}
ggplot(data, aes(x = Age, y = Averagefrequencyviolence, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("Violent Video Game Exposure") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 
```

Experiment 1: Gaming Manipulation
---------------------------------

Do men and women differ in how well they performed in the game in both self-rated (selfscore) and actual performance

```{r}
Perf <- lm(Selfscore ~  Age + Sex + VorNV + Averagefrequencyviolence + Age*VorNV + Sex*VorNV, data = data_gaming)
anova(Perf, test="Chisq")
summary(Perf, test="Chisq")

ddply(data_gaming,~Sex,summarise,mean=mean(Selfscore),sd=sd(Selfscore), se=sd(Selfscore)/sqrt(length(Selfscore)))
ddply(data_gaming,~VorNV,summarise,mean=mean(Selfscore),sd=sd(Selfscore), se=sd(Selfscore)/sqrt(length(Selfscore)))

Figure1a <- ggplot(data_gaming, aes(x = Age, y = Selfscore, color = VorNV, shape = VorNV, linetype = VorNV)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("Self-rated perception of performance") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure1b <- ggplot(data_gaming, aes(x = Averagefrequencyviolence, y = Selfscore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Exposure to violence") +
  ylab("Self-rated perception of performance") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

ggplot(data_gaming, aes(x = Age, y = Selfscore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("Self-rated perception of performance") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

multiplot (Figure1a, Figure1b, cols = 2)
##Need to find some way to standardize the scores within game category
##Nevermind...people lied with their scores so standardizing doesn't make a difference
```

##MANOVA
```{r}
MANOVA_gaming<- manova(cbind(MV1Total, SGAAverage, SOIRTOTAL) ~ VorNV + Age + Sex + Selfscore + Averagefrequencyviolence +  VorNV*Selfscore + VorNV*Sex + Age*Sex, data=data_gaming)
summary(MANOVA_gaming, test="Pillai")
summary.aov(MANOVA_gaming)
```

Plotting Mate Value and Self-score
```{r}
Figure2 <- ggplot(data_gaming, aes(x = Selfscore, y = MV1Total, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Self-rated perception of performance") +
  ylab("Mate Value") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure2
```

Plotting SGAAverage and age
```{r}
ggplot(data_gaming, aes(x = Age, y = SGAAverage, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("Sex Goal Activation") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 


```

Plotting SOIRTOTAL with Violence and Self-score
```{r}
Figure3a <- ggplot(data_gaming, aes(x = Age, y = SOIRTOTAL, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("Sociosexual Orientation Inventory") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure3b <- ggplot(data_gaming, aes(x = Selfscore, y = SOIRTOTAL, color = VorNV, shape = VorNV, linetype = VorNV)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Self-rated perception of performance") +
  ylab("Sociosexual Orientation Inventory") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

multiplot (Figure3a, Figure3b, cols = 2)

ggplot(data_gaming, aes(x = Averagefrequencyviolence, y = SOIRTOTAL, color = VorNV, shape = VorNV, linetype = VorNV)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Exposure to violence") +
  ylab("Sociosexual Orientation Inventory") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 
```

Experiment 2: Rank Manipulation
---------------------------------

Are self-scores correlated with the rank they are randomly given in the game

```{r}
selfrank_corr <- lm(Selfscore  ~  Rank + Sex + VorNV + Age + Averagefrequencyviolence + Rank*Sex + Rank*VorNV, data = data_rank)
anova(selfrank_corr, test="Chisq")

ddply(data_rank, .(Sex), summarize, mean=mean(Selfscore), se=sd(Selfscore)/sqrt(length(Selfscore)))

FigureS1a <- ggplot(data_rank, aes(x = Age, y = Selfscore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("Self-rated perception of performance") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

FigureS1b <- ggplot(data_rank, aes(x = Averagefrequencyviolence, y = Selfscore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Exposure to violence") +
  ylab("Self-rated perception of performance") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

multiplot (FigureS1a, FigureS1b, cols = 2)
```

##MANOVA
```{r}
MANOVA_rank<- manova(cbind(MV1Total, SGAAverage, SOIRTOTAL) ~ Rank + VorNV + Age + Sex + Selfscore + Averagefrequencyviolence + VorNV*Selfscore + VorNV*Rank + VorNV*Sex + Age*Sex, data=data_rank)

summary(MANOVA_rank, test="Pillai")
summary.aov(MANOVA_rank)

ddply(data_rank, .(Sex), summarize, mean=mean(SGAAverage), se=sd(SGAAverage)/sqrt(length(SGAAverage)))
ddply(data_rank, .(Sex), summarize, mean=mean(SOIRTOTAL), se=sd(SOIRTOTAL)/sqrt(length(SOIRTOTAL)))

```

```{r}
FigureS4 <- ggplot(data_rank, aes(x = Selfscore, y = MV1Total, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Selfscore") +
  ylab("Mate Value") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

ggplot(data_rank, aes(x = Rank, y = MV1Total)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Rank") +
  ylab("Mate Value") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

```

Plotting SGAAverage and age and sex
Then SGAverage and selfscore
```{r}
ggplot(data_rank, aes(x = Age, y = SGAAverage, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("Sex Goal Activation") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

ggplot(data_rank, aes(x = Selfscore, y = SGAAverage, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Self-rated perception of performance") +
  ylab("Sex Goal Activation") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

ggplot(data_rank, aes(x = Averagefrequencyviolence, y = SGAAverage, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Exposure to violence") +
  ylab("Sex Goal Activation") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

```

Plotting SOIRTOTAL with Violence and Self-score
```{r}
ggplot(data_rank, aes(x = Rank, y = SOIRTOTAL, color = VorNV, shape = VorNV, linetype = VorNV)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("Sociosexual Orientation Inventory") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

```





Experiment 3: Face Choices
---------------------------------

Do men and women differ in how well they performed in the game in both self-rated (selfscore) and actual performance

```{r}
Perf <- lm(Selfscore ~  Age + Sex + VorNV + Averagefrequencyviolence + Age*VorNV + Sex*VorNV, data = data_faces)
anova(Perf, test="Chisq")
summary(Perf, test="Chisq")

ddply(data_faces, .(Sex), summarize, mean=mean(Selfscore), se=sd(Selfscore)/sqrt(length(Selfscore)))
ddply(data_faces, .(VorNV), summarize, mean=mean(Selfscore), se=sd(Selfscore)/sqrt(length(Selfscore)))

FigureS3 <- ggplot(data_faces, aes(x = Age, y = Selfscore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("Self-rated perception of performance") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

FigureS3

##Need to find some way to standardize the scores within game category
##Nevermind...people lied with their scores so standardizing doesn't make a difference
```


##MANOVA
```{r}
MANOVA_face<- manova(cbind(MV1Total, SGAAverage, SOIRTOTAL) ~ VorNV + Age + Sex + Selfscore + Averagefrequencyviolence +  VorNV*Selfscore + VorNV*Sex + Age*Sex, data=data_faces)
summary(MANOVA_face, test="Pillai")
summary.aov(MANOVA_face)

ddply(data_rank, .(Sex), summarize, mean=mean(MV1Total), se=sd(MV1Total)/sqrt(length(MV1Total)))
ddply(data_rank, .(Sex), summarize, mean=mean(SOIRTOTAL), se=sd(SOIRTOTAL)/sqrt(length(SOIRTOTAL)))

```

Plot Mate Value
```{r}
ggplot(data_faces, aes(x = Selfscore, y = MV1Total, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Selfscore") +
  ylab("Mate Value") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

```

Looking at SGA
```{r}
ggplot(data_faces, aes(x = Averagefrequencyviolence, y = SOIRTOTAL, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("Sociosexual Orientation Inventory") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

```


```{r}
ggplot(data_faces, aes(x = Age, y = SOIRTOTAL, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("Sociosexual Orientation Inventory") +
    theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure4 <- ggplot(data_faces, aes(x=VorNV, y=SOIRTOTAL, fill=Sex)) + geom_violin() + 
  xlab("Sex") +
  ylab("Sociosexual Orientation Inventory") +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())

Figure4
```

Short term faces: 

```{r}
STselection <- lm(TotalSTScore ~  VorNV + Age + Sex + Selfscore + MV1Total + SGAAverage + SOIRTOTAL + Sex*Selfscore, data=data_faces)

anova(STselection)
```

```{r}
Figure5 <- ggplot(data_faces, aes(x = TotalSTScore, y = Selfscore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  ylim(0,7.5) +
  scale_colour_hue(l=50, guide = FALSE) +
  scale_x_continuous(limits=c(0,7.5)) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Self-rated perception of performance") +
  ylab("Short-term Facial Preference for masculinity") + 
  theme(legend.position="right") +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure5
```

```{r}
LTselection <- lm(TotalLTScore ~  VorNV + Age + Sex + Selfscore + MV1Total + SGAAverage + SOIRTOTAL + Sex*Selfscore, data=data_faces)

anova(LTselection)
```

LT Faces and age
```{r}
Figure6 <- ggplot(data_faces, aes(x = Age, y = TotalLTScore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("Age") +
  ylab("Long-term Facial Preference for masculinity") + 
  theme(legend.position="right") +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) 

Figure6

Figure7 <- ggplot(data_faces, aes(x = SOIRTOTAL, y = TotalLTScore, color = Sex, shape = Sex, linetype = Sex)) + 
  geom_point(size = 4) + 
  scale_colour_hue(l=50, guide = FALSE) +
  theme_bw() + geom_smooth(method=lm,  fullrange=T) + 
  xlab("SOI") +
  ylab("Long-term Facial Preference for masculinity") + 
  theme(legend.position="right") +
  theme(axis.line = element_line(colour = "black"),
        axis.text=element_text(size=18),
        axis.title=element_text(size=20,face="bold"),
        axis.title.y=element_text(vjust=0.25),
        axis.title.x=element_text(vjust=0.25),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
Figure7
```
-----










